---
title: "PJ Code"
output: html_notebook
---

## Library Set up

```{r}
library(data.table)
library(ggplot2)
library(sommer)
library(gplots)
library(xlsx)
```

### Phenotype data read and manipulation 

```{r}
# No option for stringsAsFactors
data_D2 <- read.xlsx("Height phenotype 20 April 2018.xlsx",sheetName = "Phenotypes April 2018",startRow = 1, as.data.frame = T)
str(data_D2)

#remove last two columns(unrequired I guess)
data_D2 <- data_D2[,1:5]
str(data_D2)

# Remove NAs
data_D2 <- data_D2[!is.na(data_D2$NA.),]
dim(data_D2)

#name ID column
data_D2$id <- data_D2$NA.

#Create positional values as factors
data_D2$Rowf <- as.factor(data_D2$Row)
data_D2$Treef <- as.factor(data_D2$Tree)
```

### SNP data read and manipulation

```{r}
# stringsAsFactors = FALSE, prevent importing as factors 
# check.names = FALSE, prevent R from adding extra values to names
# na.strings = "--", converts given na into NA
snp_D2 <- read.csv("EC103xEC201_GBS_40clusters_abxaa.csv",header=T,stringsAsFactors = FALSE, check.names = FALSE, na.strings = "--")

# Allocating numeric value to markers
snp_D2[snp_D2=="aa"] <- 0
snp_D2[snp_D2=="ab"] <- 1
snp_D2[snp_D2=="bb"] <- 2

# Remove Tree ID
snp_D2 <- snp_D2[,-1]

# Transpose, turn into a matrix
snp_M2 <- t(as.matrix(sapply(snp_D2,as.numeric)))

#Select snps from individuals present in the data_D2 matrix
snp_M2 <- snp_M2[row.names(snp_M2) %in% data_D2$id,]

#Create an A matrix (Additive relationship) and view top 10 rows and columns
A <-  A.mat(snp_M2[])
A[1:10,1:10]

#create a heatmap of relationships (maybe use another heatmap style this one bit clunky)
colfunc <- colorRampPalette(c("steelblue4","springgreen","yellow"))
heatmap.2(A[1:100,1:100], col = colfunc(100),Colv = "Rowv",revC=TRUE)
```

### Heatmap of Height Values with physical layout 

```{r}
#plot physical height distribution on the ground
ggplot(data=data_D2,aes(x=Row,y=Tree,fill=Height))+
  geom_tile()+  
  scale_fill_gradientn(colours = terrain.colors(10))
```
### Plots of heights comparing pruning groups

```{r}
#plot count
ggplot(data=data_D2,aes(x=Height,group=pruning,fill=pruning))+
  geom_histogram(alpha=0.5)

#plot density
ggplot(data=data_D2,aes(x=Height,group=pruning,fill=pruning))+
  geom_density(alpha=0.5)
```
mmer2_result <- mmer2(y ~ fixed_effect1 + fixed_effect2, random=~g(id1)+g(id2),G=list(id1=GRM1, id2=GRM2),rcov=~units, silent=TRUE, data=data,constraint=FALSE)

mmer_result <- mmer(y ~ fixed_effect1 + fixed_effect2, random=~vm(id1, Gu=GRM1)+vm(id2, Gu=GRM2),rcov=~units, silent=TRUE, data=data)

```{r}
# mmer linear mixed model fit with fixed effects and random effects. 
# spl2D fits 2D spline

mix12 <- mmer(fixed= Height ~ pruning,
                      random =~vs(id, Gu=A)
                      + Rowf
                      + Treef
                      + spl2D(Row,Tree),
                      rcov=~units,
                      data=data_D2)

summary(mix12)$varcomp
```


```{r}
fittedvals <- spatPlots(object = mix12, by= id)

vm0 <- gstat::variogram(mix12,Treef,Rowf)
plot(vm0$F1)

plot(data_D2$Height,mix12$fitted.y)

data_D2$Height_pred <- mix12$u.hat$`g(id)`$fitted.y


ggplot(data_D2,aes(x=Height,y=Height_pred,color=pruning))+
  geom_point()+labs(x="Observed tree height",y="Predicted Relative tree height")

```

## Read Data into Workspace

```{r}
corr_D2 <- read.xlsx("Similarity of individuals Joinmap calculated.xlsx",sheetIndex = 2,startRow = 1)
str(corr_D2)
```

## Potentially useful 

https://cran.r-project.org/web/packages/sommer/vignettes/v1.sommer.quick.start.pdf

