---
title: "Environmental Adjustments"
output:
  html_document:
    df_print: paged
  html_notebook: default
  pdf_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE,cache = TRUE, message = FALSE, warning = FALSE, error = FALSE)

library(data.table)
library(ggplot2)
library(sommer)
library(gplots)
library(xlsx)
library(plyr)
library(dplyr)
library(lme4)
library(plotly)
library(gridExtra)

options(stringsAsFactors=F,
         max.print = 1000,
         scipen=8,
         digits=4)
```

[Phenotype data read and manipulation F1]

[Parental Adjustments]

[Post Adjustment Plots]


### Phenotype data read and manipulation F1

```{r DataRead}
Data <- read.xlsx(file = "/powerplant/workspace/cfpmjt/leafy-green-master/Entire.xlsx", sheetName = "Sheet1",startRow = 1, as.data.frame = T)
```

```{r DataArrangement}
data_D3 = subset(Data,Allocation == "F1")
head(data_D3)

data_D3$Tree = as.numeric(data_D3$Row)
data_D3$Row = as.numeric(data_D3$Column)

data_D3 <- transform(data_D3, Treeb = substr(Tree.ID, 2,6))
data_D3$Treee = "1"
data_D3$Tree.ID = paste0(data_D3$Treee, sep = "", data_D3$Treeb)

data_D3 <- data_D3[c(1,4,7,10:12,16)]

data_D3 = distinct(data_D3)
data_D3 = data_D3[!is.na(data_D3$Chl),]

#Rename to fit into code, and factors
data_D3$id <- data_D3$Tree.ID
data_D3$Rowf <- as.factor(data_D3$Row)
data_D3$Treef <- as.factor(data_D3$Tree)

# Add pruning information
data_D2 <- read.xlsx("/powerplant/workspace/cfpmjt/leafy-green-master/Code Peter Jaksons/Height phenotype 20 April 2018.xlsx",sheetName = "Phenotypes April 2018",startRow = 1, as.data.frame = T)
D3 = data_D2[c(1,5)]
data_D3 = merge(data_D3, D3, by.x = "id", by.y = "NA.")

data_D3$measure = c(1:nrow(data_D3))

```

### SNP data read and manipulation

```{r SNP Read}
# stringsAsFactors = FALSE, prevent importing as factors 
# check.names = FALSE, prevent R from adding extra values to names
# na.strings = "--", converts given na into NA
snp_D3 <- read.csv("/powerplant/workspace/cfpmjt/leafy-green-master/Code Peter Jaksons/EC103xEC201_GBS_40clusters_abxaa.csv",header=T,stringsAsFactors = FALSE, check.names = FALSE, na.strings = "--")

# Allocating numeric value to markers
snp_D3[snp_D3=="aa"] <- 0
snp_D3[snp_D3=="ab"] <- 1
snp_D3[snp_D3=="bb"] <- 2

# Remove Tree ID
snp_D3 <- snp_D3[,-1]

# Transpose, turn into a matrix
snp_M3 <- t(as.matrix(sapply(snp_D3,as.numeric)))

#Select snps from individuals present in the data_D3 matrix
snp_M3 <- snp_M3[row.names(snp_M3) %in% data_D3$id,]
data_D3 <- data_D3[data_D3$id %in% row.names(snp_M3),]

#Create an A matrix (Additive relationship) and view top 10 rows and columns
A2 <-  A.mat(snp_M3[])
A2[1:5,1:5]
```

#### Additive Relationship Matrix

```{r Additive Matrix}
#create a heatmap of relationships (maybe use another heatmap style this one bit clunky)
colfunc <- colorRampPalette(c("steelblue4","springgreen","yellow"))
heatmap.2(A2[1:100,1:100], col = colfunc(100),Colv = "Rowv",revC=TRUE)
```

### Heatmaps of Positional Chemical Measures

#### Anthocyanin

```{r Anthocyanin Heatmap}
#plot physical height distribution on the ground
ggplot(data=data_D3,aes(x=Row,y=Tree,fill=Anth))+
  geom_tile()+  
  scale_fill_gradientn(colours = terrain.colors(10))
```

#### Chlorophyll

```{r Chlorophyll Heatmap}
ggplot(data=data_D3,aes(x=Row,y=Tree,fill=Chl))+
  geom_tile()+  
  scale_fill_gradientn(colours = terrain.colors(10))
```

#### Flavonol

```{r Flavonol Heatmap}
ggplot(data=data_D3,aes(x=Row,y=Tree,fill=Flav))+
  geom_tile()+  
  scale_fill_gradientn(colours = terrain.colors(10))
```

### Plots of heights comparing pruning groups

#### Anthocyanin

```{r Anthocyanin Pruning Effects}
#plot count
Anthplot4 = ggplot(data=data_D3,aes(x=Anth,group=pruning,fill=pruning))+
  geom_histogram(alpha=0.5, binwidth = 0.01)

Anthplot5 = ggplot(data=data_D3,aes(x=Anth,group=pruning,fill=pruning))+
  geom_density(alpha=0.5)

grid.arrange(Anthplot4,Anthplot5,ncol = 2)
```

#### Chlorophyll

```{r Chlorophyll Pruning Effects}
Chlplot4 = ggplot(data=data_D3,aes(x=Chl,group=pruning,fill=pruning))+
  geom_histogram(alpha=0.5, binwidth = 2)

Chlplot5 = ggplot(data=data_D3,aes(x=Chl,group=pruning,fill=pruning))+
  geom_density(alpha=0.5)

grid.arrange(Chlplot4,Chlplot5,ncol = 2)
```

#### Flavonol

```{r Flavonol Pruning Effects}
Anthplot4 = ggplot(data=data_D3,aes(x=Flav,group=pruning,fill=pruning))+
  geom_histogram(alpha=0.5, binwidth = 0.05)

Anthplot5 = ggplot(data=data_D3,aes(x=Flav,group=pruning,fill=pruning))+
  geom_density(alpha=0.5)

grid.arrange(Anthplot4,Anthplot5,ncol =2 )

```


### Running mmer analyses on F1 and plotting adjusted results on a positional heatmap

#### Anthocyanin

```{r Anthmmer}
# mmer linear mixed model fit with fixed effects and random effects. 
mix132 <- mmer(fixed= Anth~1,
                      random =~vs(id, Gu=A2)
                      + pruning
                      + Height
                      + Rowf
                      + Treef
                      + spl2D(Row,Tree),
                      rcov=~units,
                      data=data_D3)

plotty132 <- spatPlots(mix132,row = "Row", range = "Tree")
id = unlist(plotty132$id)
measure = unlist(plotty132$measure)
AnthAdj = unlist(plotty132$predicted.value.Anth)
AnthAdj = as.data.frame(cbind(id,AnthAdj,measure))

FData = merge(data_D3, AnthAdj, by = c("id","measure"))
FData = distinct(FData)
```

#### Chlorphyll 

```{r Chlmmer}
mix133 <- mmer(fixed= Chl~1,
                      random =~vs(id, Gu=A2)
                      + pruning
                      + Height
                      + Rowf
                      + Treef
                      + spl2D(Row,Tree),
                      rcov=~units,
                      data=data_D3)

plotty133 <- spatPlots(mix133,row = "Row", range = "Tree")
id = unlist(plotty133$id)
measure = unlist(plotty133$measure)
ChlAdj = unlist(plotty133$predicted.value.Chl)
ChlAdj = as.data.frame(cbind(id,ChlAdj,measure))

FData = merge(FData, ChlAdj, by = c("id","measure"))
```

#### Flavonol

```{r Flavmmer}
mix134 <- mmer(fixed= Flav~1,
                      random =~vs(id, Gu=A2)
                      + pruning
                      + Height
                      + Rowf
                      + Treef
                      + spl2D(Row,Tree),
                      rcov=~units,
                      data=data_D3)

plotty134 <- spatPlots(mix134,row = "Row", range = "Tree")
id = unlist(plotty134$id)
measure = unlist(plotty134$measure)
FlavAdj = unlist(plotty134$predicted.value.Flav)
FlavAdj = as.data.frame(cbind(id,FlavAdj,measure))

FData = merge(FData, FlavAdj, by = c("id","measure"))
```

```{r Combine Adj values to dataset}
Comb = ddply(FData, .(Tree.ID), summarize, Anth = mean(Anth, na.rm = T),  Chl = mean(Chl, na.rm = T), Flav = mean(Flav, na.rm = T))

FData$AnthAdj = as.numeric(FData$AnthAdj)
FData$ChlAdj = as.numeric(FData$ChlAdj)
FData$FlavAdj = as.numeric(FData$FlavAdj)


Comb2 = ddply(FData, .(Tree.ID), summarize, AnthAdj = mean(AnthAdj, na.rm = T),  ChlAdj = mean(ChlAdj, na.rm = T), FlavAdj = mean(FlavAdj, na.rm = T))


Comb3 = merge(Comb,Comb2, by = "Tree.ID")

FData2 = FData[c(1,3,4,9:12)]
FData2 = merge(FData2,Comb3, by = "Tree.ID")
FData2 = distinct(FData2)

#write.csv(FData2,"/powerplant/workspace/cfpmjt/leafy-green-master/Keep Tidy Plz/Adjusted Data2.csv")
```


#### Parental Adjustments

```{r Parent subset}
PData = subset(Data, Allocation != "F1")

PData$Tree = as.numeric(PData$Row)
PData$Row = as.numeric(PData$Column)

#Comb = ddply(PData, .(Tree.ID), summarize, Anth = mean(Anth, na.rm = T),  Chl = mean(Chl, na.rm = T), Flav = mean(Flav, na.rm = T))

PData <- PData[c(1,4,7,10:12,16)]

#PData = merge(PData,Comb, by = "Tree.ID")

PData = distinct(PData)
PData = PData[!is.na(PData$Chl),]

#remove last two columns(unrequired I guess)

str(PData)

#Rename to fit into code, and factors
PData$id <- PData$Tree.ID
PData$Rowf <- as.factor(PData$Row)
PData$Treef <- as.factor(PData$Tree)


PData$measure = c(1:nrow(PData))
```

#### Anthocyanin

```{r Panthmmer}
# mmer linear mixed model fit with fixed effects and random effects. 
# spl2D fits 2D spline
# Anthonol
mix11 <- mmer(fixed= Anth~1,
                      random =~id
                      + Height,
                      rcov=~units,
                      data=PData)
```


```{r Panthplot, include=FALSE}
plotty11 <- spatPlots(mix11,row = "Row", range = "Tree")
```


```{r anthcomb}
id = unlist(plotty11$id)
measure = unlist(plotty11$measure)
AnthAdj = unlist(plotty11$predicted.value.Anth)
AnthAdj = as.data.frame(cbind(id,AnthAdj,measure))

FData3 = merge(PData, AnthAdj, by = c("id","measure"))
```

#### Chlorophyll

```{r Pchlmmer}
mix13 <- mmer(fixed= Chl~1,
                      random =~id
                      + Height,
                      rcov=~units,
                      data=PData)
```


```{r Pchlplot, include=FALSE }
plotty13 <- spatPlots(mix13,row = "Row", range = "Tree")
```


```{r}
id = unlist(plotty13$id)
measure = unlist(plotty13$measure)
ChlAdj = unlist(plotty13$predicted.value.Chl)
ChlAdj = as.data.frame(cbind(id,ChlAdj,measure))

FData3 = merge(FData3, ChlAdj, by = c("id","measure"))
```

#### Flavonol

```{r Pflavmmer}
mix12 <- mmer(fixed= Flav~1,
                      random =~id
                      + Height,
                      rcov=~units,
                      data=PData)
```


```{r Pflavplot, include=FALSE}
plotty12 <- spatPlots(mix12,row = "Row", range = "Tree")
```


```{r}
id = unlist(plotty12$id)
measure = unlist(plotty12$measure)
FlavAdj = unlist(plotty12$predicted.value.Flav)
FlavAdj = as.data.frame(cbind(id,FlavAdj,measure))

FData3 = merge(FData3, FlavAdj, by = c("id","measure"))
```


```{r tidy Parent data}
Comb4 = ddply(FData3, .(Tree.ID), summarize, Anth = mean(Anth, na.rm = T),  Chl = mean(Chl, na.rm = T), Flav = mean(Flav, na.rm = T))

FData3$AnthAdj = as.numeric(FData3$AnthAdj)
FData3$ChlAdj = as.numeric(FData3$ChlAdj)
FData3$FlavAdj = as.numeric(FData3$FlavAdj)

Comb5 = ddply(FData3, .(Tree.ID), summarize, AnthAdj = mean(AnthAdj, na.rm = T),  ChlAdj = mean(ChlAdj, na.rm = T), FlavAdj = mean(FlavAdj, na.rm = T))

Comb6 = merge(Comb4,Comb5, by = "Tree.ID")

FData4 = FData3[c(1,3,4,9:11)]
FData4 = merge(FData4,Comb6, by = "Tree.ID")
FData4 = distinct(FData4)
```

```{r combine F1, parents and outgroup}
FData5 = FData2[-c(7)]

FData5$Allocation = "F1"

FData4$Allocation = c("CG","EC103","EC201")

FFData = rbind(FData4,FData5)

#write.csv(FFData,"/powerplant/workspace/cfpmjt/leafy-green-master/Tidy/Adjusted Data.csv")
```

#### Post Adjustment Plots

```{r Adjustment data summary}
D_data = FFData

Anth <- summary(D_data$Anth)
AnthAdj <-summary(D_data$AnthAdj)
Chl <- summary(D_data$Chl)
ChlAdj <-summary(D_data$ChlAdj)
Flav <- summary(D_data$Flav)
FlavAdj <-summary(D_data$FlavAdj)



as.table(rbind(Anth,AnthAdj,Chl,ChlAdj,Flav,FlavAdj))

```

### Anthocyanin Distribution Before and After Adjustments

```{r adj anthocyanin plots}
ggplot(D_data) + aes(x = Anth, y = AnthAdj) + geom_point(shape = 21, fill = "turquoise1") + ylab("Adjusted") + xlab("Raw") + ggtitle("Adjusted vs Raw Anthocyanin (Au)") +theme_bw()+theme(plot.title = element_text(hjust = 0.5))+ geom_smooth(method='lm')

Anth1 <- ggplot(D_data) +aes(Anth) +geom_histogram(aes(y=..density..), alpha=0.5, position="identity",colour = "turquoise3",fill ="turquoise1", binwidth = 0.001 )+ geom_density(alpha=.2,colour = "orchid1",fill = "orchid3") + ylab("Frequency") + xlab("Anthocyanin (Au)") + ggtitle("Before") +theme_bw() +theme(plot.title = element_text(hjust = 0.5)) +xlim(0.05,0.16) +ylim(0,80)

Anth2 <- ggplot(D_data) +aes(AnthAdj) +geom_histogram(aes(y=..density..), alpha=0.5, position="identity",colour = "turquoise3",fill ="turquoise1", binwidth = 0.001 )+ geom_density(alpha=.2,colour = "orchid1",fill = "orchid3") + ylab("Frequency") + xlab("Anthocyanin (Au)") + ggtitle("After") +theme_bw() +theme(plot.title = element_text(hjust = 0.5))+xlim(0.05,0.16)+ylim(0,80)

grid.arrange(Anth1,Anth2, ncol = 1)
```

### Chlorophyll Distribution Before and After Adjustments

```{r adj chlorophyll plots}
ggplot(D_data) + aes(x = Chl, y = ChlAdj) + geom_point(shape = 21, fill = "turquoise1") + ylab("Adjusted") + xlab("Raw") + ggtitle("Adjusted vs Raw Chlorophyll (Au)") +theme_bw()+theme(plot.title = element_text(hjust = 0.5))+ geom_smooth(method='lm')

Chl1 <- ggplot(D_data) +aes(Chl) +geom_histogram(aes(y=..density..), alpha=0.5, position="identity",colour = "turquoise3",fill ="turquoise1", binwidth = 0.25 )+ geom_density(alpha=.2,colour = "orchid1",fill = "orchid3") + ylab("Frequency") + xlab("Chlorophyll (g/cm2)") + ggtitle("Before") +theme_bw() +theme(plot.title = element_text(hjust = 0.5)) +xlim(24,50) +ylim(0,0.3)

Chl2 <- ggplot(D_data) +aes(ChlAdj) +geom_histogram(aes(y=..density..), alpha=0.5, position="identity",colour = "turquoise3",fill ="turquoise1", binwidth = 0.25 )+ geom_density(alpha=.2,colour = "orchid1",fill = "orchid3") + ylab("Frequency") + xlab("Chlorophyll (g/cm2)") + ggtitle("After") +theme_bw() +theme(plot.title = element_text(hjust = 0.5)) +xlim(24,50)+ylim(0,0.3)

grid.arrange(Chl1,Chl2, ncol = 1)
```

### Flavonol Distribution Before and After Adjustments

```{r adj flavonol plots}
ggplot(D_data) + aes(x = Flav, y = FlavAdj) + geom_point(shape = 21, fill = "turquoise1") + ylab("Adjusted") + xlab("Raw") + ggtitle("Adjusted vs Raw Flavonols (Au)") +theme_bw()+theme(plot.title = element_text(hjust = 0.5))+ geom_smooth(method='lm')

Flav1 <- ggplot(D_data) +aes(Flav) +geom_histogram(aes(y=..density..), alpha=0.5, position="identity",colour = "turquoise3",fill ="turquoise1",binwidth = 0.01 )+ geom_density(alpha=.2,colour = "orchid1",fill = "orchid3") + ylab("Frequency") + xlab("Flavonol (Au)") + ggtitle("Before") +theme_bw() +theme(plot.title = element_text(hjust = 0.5)) +xlim(1.5,2.4) +ylim(0,8)

Flav2 <- ggplot(D_data) +aes(FlavAdj) +geom_histogram(aes(y=..density..), alpha=0.5, position="identity",colour = "turquoise3",fill ="turquoise1",binwidth = 0.01  )+ geom_density(alpha=.2,colour = "orchid1",fill = "orchid3") + ylab("Frequency") + xlab("Flavonol (Au)") + ggtitle("After") +theme_bw() +theme(plot.title = element_text(hjust = 0.5))+xlim(1.5,2.4)+ylim(0,8)

grid.arrange(Flav1,Flav2, ncol = 1)
```

## Comparison of Allocations

Allocation is the grouping of trees in the dataset, F1 refers to the cross of the parents EC103 and EC201. CG is an outgroup of Crimson Glory


### Before and After Plots Comparison Between Allocations

#### Anthocyanin


```{r anth allocation plots}
Anthplot = ggplot(D_data, aes(Allocation,Anth)) +geom_violin(fill = "turquoise1") + ggtitle("Before")+ stat_summary(fun=mean, colour="black",fill = "orchid1", geom="point", shape=23, size=3) +ylab("Anthocyanin (Au)") +xlab("Allocation")+theme_bw() +ylim(0.05,0.26)

Anthplot2 = ggplot(D_data, aes(Allocation,AnthAdj)) +geom_violin(fill = "turquoise1") + ggtitle("After")+ stat_summary(fun=mean, colour="black",fill = "orchid1", geom="point", shape=23, size=3) +ylab("Anthocyanin (Au)") +xlab("Allocation")+theme_bw() +ylim(0.05,0.26)

grid.arrange(Anthplot,Anthplot2, ncol = 2)
```

#### Chlorophyll

```{r chl allocation plots}
Chlplot = ggplot(D_data, aes(Allocation,Chl)) +geom_violin(fill = "turquoise1") + ggtitle("Before")+ stat_summary(fun=mean, colour="black",fill = "orchid1", geom="point", shape=23, size=3) +ylab("Chlorophyll (g/cm2)") +xlab("Allocation")+theme_bw()+ylim(23,53)

Chlplot2 = ggplot(D_data, aes(Allocation,ChlAdj)) +geom_violin(fill = "turquoise1") + ggtitle("After")+ stat_summary(fun=mean, colour="black",fill = "orchid1", geom="point", shape=23, size=3) +ylab("Chlorophyll (g/cm2)") +xlab("Allocation")+theme_bw()+ylim(23,53)

grid.arrange(Chlplot,Chlplot2,ncol = 2 )
```

#### Flavonol

```{r flav allocation plots}
Flavplot = ggplot(D_data, aes(Allocation,Flav)) +geom_violin(fill = "turquoise1") + ggtitle("Before")+ stat_summary(fun=mean, colour="black",fill = "orchid1", geom="point", shape=23, size=3) +ylab("Flavonol (Au)") +xlab("Allocation")+theme_bw()+ylim(1.5,2.5)

Flavplot2 = ggplot(D_data, aes(Allocation,FlavAdj)) +geom_violin(fill = "turquoise1") + ggtitle("After")+ stat_summary(fun=mean, colour="black",fill = "orchid1", geom="point", shape=23, size=3) +ylab("Flavonol (Au)") +xlab("Allocation")+theme_bw()+ylim(1.5,2.5)

grid.arrange(Flavplot,Flavplot2,ncol = 2)
```

```{r}
grid.arrange(Anthplot,Anthplot2,Chlplot,Chlplot2,Flavplot,Flavplot2, ncol = 2)
```

