---
title: "PJ Code"
output: html_notebook
---

## Library Set up

```{r}
library(data.table)
library(ggplot2)
library(sommer)
library(gplots)
library(xlsx)
library(plyr)

options( stringsAsFactors=F,
         max.print = 1000,
         scipen=8,
         digits=4)
```

### Phenotype data read and manipulation 

```{r}
Data <- read.xlsx(file = "Entire.xlsx", sheetName = "Sheet1",startRow = 1, as.data.frame = T)
data_D3 = subset(Data,Allocation == "F1")
str(data_D3)

data_D3$Tree = as.numeric(data_D3$Row)
data_D3$Row = as.numeric(data_D3$Column)

data_D3 <- transform(data_D3, Treeb = substr(Tree.ID, 2,6))
data_D3$Treee = "1"
data_D3$Tree.ID = paste0(data_D3$Treee, sep = "", data_D3$Treeb)

Comb = ddply(data_D3, .(Tree.ID), summarize, Anth = mean(Anth, na.rm = T),  Chl = mean(Chl, na.rm = T), Flav = mean(Flav, na.rm = T))

data_D3 <- data_D3[,c(1,4,8,16)]

data_D3 = merge(data_D3,Comb, by = "Tree.ID")

data_D3 = distinct(data_D3)
data_D3 = data_D3[!is.na(data_D3$Chl),]

#remove last two columns(unrequired I guess)

str(data_D3)

#Rename to fit into code, and factors
data_D3$id <- data_D3$Tree.ID
data_D3$Rowf <- as.factor(data_D3$Row)
data_D3$Treef <- as.factor(data_D3$Tree)


```

### SNP data read and manipulation

```{r}
# stringsAsFactors = FALSE, prevent importing as factors 
# check.names = FALSE, prevent R from adding extra values to names
# na.strings = "--", converts given na into NA
snp_D3 <- read.csv("EC103xEC201_GBS_40clusters_abxaa.csv",header=T,stringsAsFactors = FALSE, check.names = FALSE, na.strings = "--")

# Allocating numeric value to markers
snp_D3[snp_D3=="aa"] <- 0
snp_D3[snp_D3=="ab"] <- 1
snp_D3[snp_D3=="bb"] <- 2

# Remove Tree ID
snp_D3 <- snp_D3[,-1]

# Transpose, turn into a matrix
snp_M3 <- t(as.matrix(sapply(snp_D3,as.numeric)))

#Select snps from individuals present in the data_D3 matrix
snp_M3 <- snp_M3[row.names(snp_M3) %in% data_D3$id,]
data_D3 <- data_D3[data_D3$id %in% row.names(snp_M3),]

#Create an A matrix (Additive relationship) and view top 10 rows and columns
A2 <-  A.mat(snp_M3[])
A2[1:10,1:10]

#create a heatmap of relationships (maybe use another heatmap style this one bit clunky)
colfunc <- colorRampPalette(c("steelblue4","springgreen","yellow"))
heatmap.2(A2[1:100,1:100], col = colfunc(100),Colv = "Rowv",revC=TRUE)
```

### Heatmap of Height Values with physical layout 

```{r}
#plot physical height distribution on the ground
ggplot(data=data_D3,aes(x=Row,y=Tree,fill=Chl))+
  geom_tile()+  
  scale_fill_gradientn(colours = terrain.colors(10))
```
### Plots of heights comparing pruning groups

```{r}
#plot count
ggplot(data=data_D3,aes(x=Height,group=pruning,fill=pruning))+
  geom_histogram(alpha=0.5)

#plot density
ggplot(data=data_D3,aes(x=Height,group=pruning,fill=pruning))+
  geom_density(alpha=0.5)
```
mmer2_result <- mmer2(y ~ fixed_effect1 + fixed_effect2, random=~g(id1)+g(id2),G=list(id1=GRM1, id2=GRM2),rcov=~units, silent=TRUE, data=data,constraint=FALSE)

mmer_result <- mmer(y ~ fixed_effect1 + fixed_effect2, random=~vm(id1, Gu=GRM1)+vm(id2, Gu=GRM2),rcov=~units, silent=TRUE, data=data)

```{r}
# mmer linear mixed model fit with fixed effects and random effects. 
# spl2D fits 2D spline

mix13 <- mmer(fixed= Anth~1,
                      random =~vs(id, Gu=A2)
                      + Rowf
                      + Treef
                      + spl2D(Row,Tree),
                      rcov=~units,
                      data=data_D3)

summary(mix13)
```


```{r}
fittedvals <- spatPlots(object = mix13, by= id)

vm0 <- gstat::variogram(mix12,Treef,Rowf)
plot(vm0$F1)

plot(data_D3$Height,mix12$fitted.y)

data_D3$Height_pred <- mix12$u.hat$`g(id)`$fitted.y


ggplot(data_D3,aes(x=Height,y=Height_pred,color=pruning))+
  geom_point()+labs(x="Observed tree height",y="Predicted Relative tree height")

```

## Read Data into Workspace

```{r}
corr_D2 <- read.xlsx("Similarity of individuals Joinmap calculated.xlsx",sheetIndex = 2,startRow = 1)
str(corr_D2)
```

## Potentially useful 

https://cran.r-project.org/web/packages/sommer/vignettes/v1.sommer.quick.start.pdf

