---
title: "Replicate Analysis"
author: "Melissa Taane"
date: "12/1/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE,cache = TRUE, message = FALSE, warning = FALSE)
library(xlsx)
library(ggplot2)
library(gplots)
library(gridExtra)
library(corrplot)
library(plyr)
library(dplyr)
library(png)
library(grid)
library(heatmaply)
library(lme4)
library(MCMCglmm)
library(tidyverse)
library(broom)
library(nadiv)
library("glmnet") 
library("caret")
library("ggcorrplot")
library(factoextra)
library(fpc)
```

#### Background

The point of the replicate process was to establish how reliable the results were from the dualex. A leaf from each tree was measured twice, having been removed between measurements. 
The distribution of chemicals within a given leaf can be variable, thus it would be unlikely to replicate each measurement exactly as the dualex will measure a different part of the leaf. 

[Overview]

[Anthocyanin]

[Chlorophyll]

[Flavonol]


```{r data read and organisation}
# Read in data, organise data

Rep <-read.xlsx("/powerplant/workspace/cfpmjt/leafy-green-master/Full.xlsx", sheetName ="Dup")

Rep1 = subset(Rep, Rep. == "Y1")
Rep2 = subset(Rep, Rep. == "Y2")

colnames(Rep1) <- paste("Rep1", colnames(Rep1 ), sep = "_")
colnames(Rep2) <- paste("Rep2", colnames(Rep2), sep = "_")

Rep3 = merge(Rep1,Rep2, by.x = c("Rep1_Tree.ID","Rep1_Height","Rep1_group"),by.y=  c("Rep2_Tree.ID","Rep2_Height","Rep2_group"))
```

### Overview

#### Plots of Replicate Chemical Distribution


```{r}
plot1 = ggplot(Rep, aes(Rep., Anth)) +geom_boxplot(fill = "turquoise1") + ggtitle("Anthocyanin")+ stat_summary(fun.y=mean, colour="black", geom="point", shape=23, size=3, fill = "white")+ geom_jitter(shape=21, position=position_jitter(0.2), fill = "orchid1")+theme_bw() +ylab("Anthocyanin (Au)") +xlab("Replicate")

plot2 = ggplot(Rep, aes(Rep., Chl)) +geom_boxplot(fill = "turquoise1") + ggtitle("Chlorphyll")+ stat_summary(fun.y=mean, colour="black", geom="point", shape=23, size=3, fill = "white")+ geom_jitter(shape=21, position=position_jitter(0.2), fill = "orchid1")+theme_bw() +ylab("Chlorophyll (g/cm2)")+xlab("Replicate")

plot3 = ggplot(Rep, aes(Rep., Flav)) +geom_boxplot(fill = "turquoise1") + ggtitle("Flavonol")+ stat_summary(fun.y=mean, colour="black", geom="point", shape=23, size=3, fill = "white")+ geom_jitter(shape=21, position=position_jitter(0.2), fill = "orchid1")+theme_bw() +ylab("Flavonol (Au)")+xlab("Replicate")

grid.arrange(plot1,plot2,plot3,ncol=3)

```

#### Data

```{r data summary}
Rep1Anth = summary(Rep1$Rep1_Anth)
Rep2Anth = summary(Rep2$Rep2_Anth)
Rep1Chl = summary(Rep1$Rep1_Chl)
Rep2Chl = summary(Rep2$Rep2_Chl)
Rep1Flav = summary(Rep1$Rep1_Flav)
Rep2Flav = summary(Rep2$Rep2_Flav)

as.table(rbind(Rep1Anth,Rep2Anth,Rep1Chl,Rep2Chl,Rep1Flav,Rep2Flav))
```

#### Anthocyanin

```{r anthocyanin plots}
# dotplot
ggplot(Rep3) + aes(x = Rep1_Anth, y = Rep2_Anth) + geom_point(shape = 21, fill = "turquoise1") + ylab("Replicate 2") + xlab("Replicate 1") + ggtitle("Replicate Anthocyanin (Au) Measures") +theme_bw()+theme(plot.title = element_text(hjust = 0.5))+ geom_smooth(method='lm', colour = "orchid1")

# boxplot
ggplot(Rep, aes(Rep.,Anth)) +geom_violin(fill = "turquoise1") + ggtitle("Anthocyanin Measurements Distributions for Replicates")+ stat_summary(fun=mean, colour="black",fill = "orchid1", geom="point", shape=23, size=3) +ylab("Anthocyanin (Au)") +xlab("Replicate")+theme_bw() +ylim(0.05,0.26)

# anova
Anthmod = lm(Rep$Anth ~ Rep$Rep.)
anova(Anthmod)
```

#### Chlorophyll

```{r chlorophyll plots}
# dotplot
ggplot(Rep3) + aes(x = Rep1_Chl, y = Rep2_Chl) + geom_point(shape = 21, fill = "turquoise1") + ylab("Replicate 2") + xlab("Replicate 1") + ggtitle("Replicate Chlorophyll(g/cm2) Measures") +theme_bw()+theme(plot.title = element_text(hjust = 0.5))+ geom_smooth(method='lm', colour = "orchid1")

# boxplot
ggplot(Rep, aes(Rep.,Chl)) +geom_violin(fill = "turquoise1") + ggtitle("Chlorophyll Measurements Distributions for Replicates")+ stat_summary(fun=mean, colour="black",fill = "orchid1", geom="point", shape=23, size=3) +ylab("Chlorophyll (g/cm2)") +xlab("Replicate")+theme_bw() 

# anova
Chlmod = lm(Rep$Chl ~ Rep$Rep.)
anova(Chlmod)
```

#### Flavonol

```{r flavonol plots}
# dotplot
ggplot(Rep3) + aes(x = Rep1_Flav, y = Rep2_Flav) + geom_point(shape = 21, fill = "turquoise1") + ylab("Replicate 2") + xlab("Replicate 1") + ggtitle("Replicate Flavonol (Au) Measures") +theme_bw()+theme(plot.title = element_text(hjust = 0.5))+ geom_smooth(method='lm', colour = "orchid1")

# boxplot
ggplot(Rep, aes(Rep.,Flav)) +geom_violin(fill = "turquoise1") + ggtitle("Flavonol Measurements Distributions for Replicates")+ stat_summary(fun=mean, colour="black",fill = "orchid1", geom="point", shape=23, size=3) +ylab("Flavonol (Au)") +xlab("Replicate")+theme_bw()

# anova
Flavmod = lm(Rep$Flav ~ Rep$Rep.)
anova(Flavmod)
```





